Forecasting the 2024 U.S. Presidential Election: Polling Trends and Dynamics Based on National General Election Polls

### 2024-11-04 paper/paper.qmd

library(tidyverse)
library(usmap)
library(dplyr)
library(here)
library(ggplot2)
library(janitor)
library(knitr)
library(flextable)
```

# Load the cleaned dataset for use in this section
analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")

@@

```{r}
# Visualization: Distribution of Sample Sizes
library(ggplot2)
ggplot(analysis_data, aes(x = sample_size)) +
  geom_histogram(binwidth = 100, fill = "skyblue", color = "black") +
  labs(title = "Distribution of Sample Sizes in Polls", 
       x = "Sample Size", 
       y = "Frequency") +
  theme_minimal()
```

>>>>

library(tidyverse)
library(usmap)
library(dplyr)
library(here)
library(ggplot2)
library(janitor)
library(knitr)
library(flextable)
library(arrow)
```

# Load the cleaned dataset for use in this section
analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")

@@

```{r visualize-sample-size}
# Ensure 'analysis_data' is already loaded at this point
ggplot(analysis_data, aes(x = sample_size)) +
  geom_histogram(binwidth = 100, fill = "skyblue", color = "black") +
  labs(title = "Distribution of Sample Sizes in Polls", 
       x = "Sample Size", 
       y = "Frequency") +
  theme_minimal()

```
